An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-07-05 poly-embed-journal/poly-embed-journal.tex
Clean up tex

The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general}\raft{TODO: see if there are other references we should include here.  Maybe Jessie you could search?}.
Intuitively, a loss is non-redundant if no report is weakly dominated by another report.

@@

\section{The one lemma to save them all}

\jessie{Lemma X}
\begin{lemma}
	Let $f: \simplex \to \reals_+$ be a (concave) polyhedral function.
	There exists a unique set of loss vectors $\V^*$ of minimum cardinality such that $f(p) = \min_{v \in \V^*} \inprod{v}{p}$ for all $p\in\simplex$.
	Define $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$, and $\Theta := \{\theta(v) \mid v \in \V^*\}$.
	Furthermore, let $L: \R \to \reals^\Y_+$ be any loss whose infimum is attained with Bayes risk $\risk L=f$ and let $\Gamma := \prop{L}$.
	Then $L$ has a finite minimum representative set, and for any minimum representative set $\R^* \subseteq \R$,
	\begin{enumerate}
		\item $\{L(r^*) \mid r^* \in \R^*\} = \V^*$,
		\item $\{\Gamma_r \mid r \in \R^*\} = \Theta$ is exactly the set of full-dimensional level sets of $\Gamma$\jessie{relative to $\reals^{n-1}$},
		\item For any $r \in \R$, there exists $r^* \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r^*}$\jessie{power diagrams stuff}.
	\end{enumerate}
\end{lemma}

\raf{Recommend a general definition of $H_v$ and $H_v^+$ for $v\in\reals^\Y$; recommend avoiding $h\in\reals^\Y$}

Phase 1: construct $\V^*$. 
\jessie{In appendix, try to flesh out phase 1.  Follow (and note) textbook(s) where definitions come from}
\jessie{Definitions coming from Ziegler Lectures on Convex Polytopes unless otherwise noted}
\jessie{Lecture notes on $H$-redundancies found in Chapter 8 here: \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
\jessie{$\delta(x\mid C)$ is the $0-\infty$ indicator if $x \in C$.}
\jessie{Introduce general notation upfront}
\jessie{Strike a balance between things you know are true but need citations for, and having a fully fleshed out argument.  Don't block on finding the right reference.}

By Rockafellar, we have $f$ polyhedral if and only if it can be written as the max of a finite set of linear functions $\V$ over $\reals^\Y_+$. 
Therefore, $f(p) = \min_{v\in\V} \inprod{p}{v}$ over $p \in \reals_+^\Y$. 
We extend $f$ to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = \infty$ otherwise, and define $g(0) = 0$. 
That is, $g(x) = \min_{v \in \V} \inprod{x}{v} + \delta(x \mid \reals^\Y_+)$, which is also polyhedral by Rockafellar. 
Note that $g$ and $f$ match on $\reals^\Y_+$.
Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$ as the hypograph of $g$.

Let $H_{v}^+ := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c \geq 0\}$ as the halfspace generated by a vector $v$ and $H_{v} := \{ (x,c) \in \reals^\Y \times \reals \mid \inprod{x}{v} - c = 0\}$ and as the hyperplane defining the boundaries of this halfspace.
Abusing notation, we will say $H_y^+ := \{(x,c) \mid x_y \geq 0\}$, and $H_y := \{(x,c) \mid x_y = 0\}$ for $y \in \Y$. %\jessie{$H_y = H_{e_y}$ doesn't quite match up with what was here before; before, $H^+_y\{(x,c) \mid x_y \geq 0\}$, where this now has a $-c$ in that term.}
For any set of vectors, $Z$, let $\H_{Z} = \{H_z^+ \mid z\in Z\}$, and denote $\H = \H_{\V} \cup \H_\Y$\footnote{Slightly abusing notation, we denote $\H_\Y := \{H_y \mid y \in \Y\}$} as the set of halfspaces defining $G$; $\H_{\hat V}$ defines $G$ on $\reals^\Y_+$, and $\H_\Y$ determines $G$ outside  the nonnegative orthant.
Then $G = \cap \H$, and is full-dimensional, e.g., $\dim(\affhull(G)) = n$.
Since $G$ is a full-dimensional polyhedron, it has a $H$-rep $H'$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes}.
Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
%Consider the set $\V^* := H' \setminus e_\Y$\footnote{$e_\Y := \{e_i\}_{i=1}^n$}. \jessie{Doesn't quite type check, hence the comment out}
We argue $\H_\Y \subseteq \H'$; if there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H'$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H'$, or we have a point $x$ such that $x_y < 0$ but $g(x) < \infty$.
The first cannot happen as we take $f$ to be defined (and finite) on $\reals_+^\Y$, and $f$ and $g$ match on the domain of $f$.
Moreover, the second cannot be true by construction of $g$.
Therefore, we have $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V \subseteq \V^*$.

$\V^*$ is precisely the set we are looking for; it is uniquely generated by $f$ since $\H'$ and $\H_\Y$ are unique, and minimum cardinality since $\H'$ has minimum cardinality \jessie{Since it has finite cardinality and uniquely determines $g$}.  
Moreover, $F_v := H_v \cap G$ is a facet of $G$ for each $v\in\V^*$~\citep[Proposition 4.5]{gallier2008notes}. 
%\jessie{by analog of Ziegler Theorem 2.15; more directly by Gallier notes \url{https://arxiv.org/pdf/0805.0292.pdf} Prop 4.5}

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
We can write any face $F_v = \{x \in \reals^\Y \mid \inprod{x}{v} = g(x)\}$.
We claim $\cup_{v \in \V^*}\pi(F_v) = \reals_+^\Y$.
If there was a $v \in \V^*$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
Thus, $\cup_{v \in \V^*} \pi(F_v) \subseteq \reals_+^\Y$.
Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V^*}\inprod{v}{x}$, so there is a $v \in \V^*$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V^*$, and is therefore in the union of projections.
As we have shown both directions of set inclusion, we must have $\cup_{v \in \V^*}\pi(F_v) = \reals_+^\Y$.
Note that we can also take $\theta(v) = F_v \cap \simplex$.

@@

\begin{claim}\label{claim:projected-faces-cover-RY-iff-representative}
  A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
\end{claim}
\begin{proof}
raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}

>>>>

The condition that a representative set be minimum implies that one has identified exactly the ``active'' reports of a loss, in some sense.
We now relate this condition to another natural notion from the property elicitation literature, that of non-redundancy~\cite{frongillo2014general,lambert2018elicitation}\raft{TODO: see if there are other references we should include here.  Maybe Jessie you could search? \jessie{Quick search leads me to a couple of your papers and Nico's, but not much else.}}.
Intuitively, a loss is non-redundant if no report is weakly dominated by another report.

@@

@@

\begin{claim}\label{claim:projected-faces-cover-RY-iff-representative}
  A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
\end{claim}
\begin{proof}
\raf{Need 1-homog here -- suggest separating out statement like cone(simplex cap pi(Fv)) = pi(Fv)}
